A new type of automated prover based on category theory

### 2022-08-07 paper.tex
Minor fixes
Change some from pmb to textbf

%% Copyright 2022 Zijian Wang. All rights reserved.
%% Email: felix_wzj@yahoo.com

@@

To avoid misunderstandings, \pmb{the Zermelo-Fraenkel set theory} or ZFC as short is utilized to be the set system, with Grothendieck universe concepts added. \cite{1}

@@

Before more specific discussion, we select Grothendieck universe \(\mathcal{U}\) \cite{1} to avoid set theory paradoxes. Besides, we define meta category \(\mathcal{C}\) where all discussions take place. There are briefly three kind of objects in \(\mathcal{C}\): symbols, notations and brackets. All symbols in \(\mathcal{C}\) forms sub category \(\text{Sym}(\mathcal{C})\) called the \pmb{ Symbol Subcategory}. All notations in \(\mathcal{C}\) forms \(\text{Not}(\mathcal{C})\) and all brackets forms \(\text{Bra}(\mathcal{C})\), called the \pmb{ Notation Subcategory} and the \pmb{ Bracket Subcategory}. That is,

@@

\pmb{ Definition.} A \pmb{ bracket} \(\beta\) is defined as a set of ordered pairs in the form of below:

@@

\(\beta\) is valid if and only if every element of \(\beta\), its left element is unique. We define filtered subsets of \(\beta\). The \pmb{ Symbol Subset} of \(\beta _{\mathcal{S}}\text{:=}\left\{t\in \beta \left|t_{\mathit{r}}\in \text{Sym}(\mathcal{C})\right.\right\}\). Following this way, the \pmb{ Notation Subset} \(\beta _{\mathcal{N}}\) and the \pmb{ Bracket Subset} \(\beta _{\mathcal{B}}\) are defined as well. There are two types of brackets: The first type is called a \pmb{ Symbol Holder} where \(\beta =\{(i,A)\},i\in \mathbb{Z}_{\geq 1},A\in \text{Sym}(\mathcal{C})\). The second type is called a \pmb{ Compositor} where

@@

\pmb{ Definition.} Two bracket \(\alpha\) and \(\beta\), are thought to be \pmb{ isomorphic} (noted as \(\alpha \simeq \beta\)) if they satisfy the following restrictions:

First, \(|\alpha |=|\beta |\) indicating the two brackets have same cardinal numbers. Second, all right elements sorted in the order defined by the sort of the left pair elements, correspondingly, are either same or symbols with the same type. Otherwise, the two brackets are \pmb{ not isomorphic}, noted as \(\alpha \not{\simeq}\beta\).

@@

\pmb{ Definition.} A \pmb{ notation} \(\mathcal{N}\) is defined as an object in \(\text{Not}(\mathcal{C})\) which is a sub category of \(\mathcal{C}\). The \(\text{Ob}(\text{Not}(\mathcal{C}))\) set can be mapped to \(\text{On}_{\geq 0}\) class, indicating the number of parameters that a notation take. In which,

@@

In that case if \(n=0\) then we say \(\mathcal{N}\) is a \pmb{ type} and if \(n>0\) then \(\mathcal{N}\) is an \pmb{ operator}. For instance, obviously, \(\mathit{p}(+)=2\) and \(\mathit{p}(\neg )=1\). A notation\(\mathcal{N}\) is called \pmb{ finite} if \(\mathit{p}(\mathcal{N})<\omega\), and otherwise \(\mathcal{N}\) can have infinite number of symbols as parameters, when the notation is called to be \pmb{ infinite}.

@@

\pmb{ Definition.} A \pmb{ symbol} \(\mathcal{S}\) is defined as an object in \(\text{Sym}(\mathcal{C})\) which is a sub category of \(\mathcal{C}\). There exists a functor from \(\text{Sym}(\mathcal{C})\) to \(\text{Not}(\mathcal{C})\):

@@

Where \(\nu (\mathcal{S})\) is the \pmb{ corresponding notation} of \(\mathcal{S}\) and must satisfy \(\forall \mathcal{S}\in \text{Sym}(\mathcal{C}),\mathit{p}(\nu (\mathcal{S}))=0\), indicating all corresponding notations are types instead of operators. For convenience and precision, the text that meaning creating a symbol \(\mathcal{S}\) whose corresponding notation is \(\mathcal{N}\)can and should be written in the form below.

@@

Two brackets are thought to be \pmb{ equal} when the sequences of \(t_{\mathit{r}}\), sorted via the ordering of \(t_{\ell }\) are the same and this relationship constructs a equivalence morphism between the two in the \(\text{Bra}(\mathcal{C})\) category, noted as below:

@@

\pmb{ Definition.} A notation \(\mathcal{N}\) is called being \pmb{ inherited} from notation \(\mathcal{M}\) (or we say \(\mathcal{N}\) is\pmb{  a kind of} \(\mathcal{M}\)) when there exists such morphism between the two in \(\text{Not}(\mathcal{C})\):

@@

\[\alpha =\{(0,\text{for}),(1,\beta ),(2,\{(0,<),(1,\{(0,\text{abs}),(1,\pmb{x})\}),(2,\pmb{1})\})\}\]
\[\beta =\{(0,=),(1,\delta ),(2,\{(0,/),(1,\pmb{1}),(2,\{(0,-),(1,\pmb{1}),(2,\pmb{x})\})\})\}\]
\[\delta =\{(0,\sum ),(1,\{(0,=),(1,\pmb{n}),(2,\pmb{1}\pmb{)}\pmb{\}}),(2,\pmb{\infty }), (3,\{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\})\}\]

@@

Another issue is about the recognition between majorly two types of brackets: the type of bracket that purely serves as a brick for constructing mathematical expressions and the type of bracket that forms the thing that former mathematics call them statements (for instance, \(\{(0,=),(1,x),(2,y)\}\) or the expression for the Pythagorean theorem). In this system for representation, the second sort of bracket is called \pmb{ micro-statements}, whose precise definition comes below.

@@

It is essential to pay attention to that a bracket with 2-parameter notation is not necessarily a micro-statement. This conclusion can be illustrated via the example of \(\{(0,+),(1,x),(2,y)\}\) whose notation has two symbols as parameters but is not a micro-statement. The second restriction is more important, which is that a micro-statement must have the capacity to be evaluated into a Boolean value, that is, \(\text{true}\) or \(\text{false}\). What is notable, the \pmb{ evaluation} process is not declared inside the representation system, whose definition comes below. All micro-statement brackets forms the \pmb{ Micro-Statement }sub category of \(\text{Bra}(\mathcal{C})\) and is annotated as \(\text{Mic}(\mathcal{C})\).

@@

The Boolean value \(\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m})\in \{0,1\}\) is called the \pmb{ evaluation result} of micro-statement. If for bracket \(\mathit{m}\) exists a morphism to \(\mathcal{B}\) that satisfies the definition of evaluation, then we say that \(\mathit{m}\) is \pmb{ evaluatable}. That is, if it satisfies the first restriction of being a micro-statement as well, it is a micro-statement.

@@

The discussion below calls the \(\text{Mic}(\mathcal{C})\) category the \pmb{ micro-statement pool}, or \pmb{ pool} for short. The morphisms inside the micro-statements pool are declared for representation of implication relationships. It is obvious are elementary that,

@@

\pmb{ Definition.} A \pmb{ derivation} is a set of ordered pairs of ordinals and categories in the form below.

@@

Where \(\mathcal{M}_i\) { }is a micro-statement pool and for each element in \(\mathcal{D}\), its left pair element is a unique ordinal. The $\mathcal{D}$ set is well-ordered following the sort of \(i\). On the beginning, the the initial pool equals to the condition, that is the micro-statements given by the problem. On the other hand, the conclusions of the proof problem, to be proved via some steps form a set \(\mathcal{R}\), called the \pmb{requirement set} are to be inferred to exist inside the micro-statement pool.

@@

\pmb{ Definition.} A \pmb{ step of derivation} is a map existed on the derivation set \(\mathcal{D}\), mapping from a pair to another, whose ordinal increases by \(1\). This map is annotated using script word \(\mathit{s}\mathit{t}\mathit{e}\mathit{p}\). The form is shown below:

@@

Inside the map, the left pair element is simply self-increased and the right pair element is processed by a functor (since the item to process is a category) called the \pmb{ recurse functor} noted as \(\mathcal{F}_i\). That is,

@@

\pmb{ Definition.} A derivation set is thought to be \pmb{ successful} when the condition below is satisfied when the condition below is true:

@@

On the other hand, a derivation set is thought to be \pmb{ impossible} when there does not exist such a \(n\in [0,\omega )\) that makes the requirement set a subset of the object set of the targeted micro-statement pool.

@@

\pmb{ Definition. }A \pmb{ reflection functor} \(\mathcal{K}\) is defined as an functor object in a functor category \(\mathcal{R}\mathit{e}\mathit{f}\), who maps between two micro-statement pools. Because of the Zermelo{'}s Well-Ordering Theorem we mentioned in the Preliminary section, \(\text{Ob}(\mathcal{R}\mathit{e}\mathit{f})\) can be put into well-order, with ordinal \(i\). All of the reflection functors forms a functor category \(\mathcal{Q}\), called the \pmb{ reflection knowledge base}, or for short the \pmb{ knowledge base}. The detailed explanation and description, including the utilization of and morphisms inside the knowledge base, will be discussed later in this section of the paper. We annotate each of the functor positioned at location \(i\) with \(\mathcal{K}_i\).

Each reflection functor corresponds to a \pmb{ template pair} of micro-statements \((\sigma ,\tau )\) which indicates that the effect of the functor is to transform micro-statement \(\sigma\) into $\tau $. The template pair of functor \(\mathcal{K}\) is annotated with \(T(\mathcal{K})\). That
is,

@@

When reflection functor \(\mathcal{K}_i\) is applied to a pool \(\mathcal{M}_i\), each of the micro-statements in the object set of the pool is proceeded. If a micro-statement is suitable for the reflection, whose detailed explanation will be discussed later, a new micro-statement will be created if there{'}s no duplication. Then a morphism will be built from the old micro-statement to the new item. The process of identifying whether a micro-statement is capable called an \pmb{ isomorphism inspection} is described as below.

\pmb{ Definition.} The process of isomorphism inspection is declared as below. The stuff that the isomorphism inspection process manipulates is a micro-statement \(\mu \in \mathcal{M}_i\), a special evaluatable sort of bracket. The definition of bracket being isomorphic can be found in the second section. Explicitly, the inspection process is to construct a new set called the \pmb{ transformation source}, noted as \(\text{Ts}\) using the equation below.

@@

What to do next is called a \pmb{ transformation}. Foremost, creates a set of transformation rules that makes one-one maps the micro-statement to manipulate to the left of the template pair \(\sigma\). Secondarily, the reverse map is applied to the right of the template pair \(\tau\) and then the transformation process execution is done. Then we delineate the definition of { }transformation mapping.

\pmb{ Definition.} A \pmb{ transformation map} is a one-one map defined between the list of symbol and sub-brackets of the two brackets \(\alpha\) and \(\beta\) where,

@@

To begin with, the translation map between the two temporary sets, that is each of the elements of transformation source and the left element of the template pair, are constructed forming an executable rule that makes each non-notation right pair element \(x\) in \(\mu \epsilon \mathcal{M}_i\), which is a micro-statement to discuss, to have \(\mathcal{T}(x)\in \sigma _{\mathcal{B}}\cup \sigma _{\mathcal{S}}\). After the construction, we execute a \pmb{ reverse transformation } from \(\tau\) to a new micro-statement \(\mu '\) satisfying that

@@

\pmb{ Definition. }The \pmb{ initial map }is the original state of knowledge base \(\mathcal{Q}\) when \(\mathcal{Q}\) is created. Initially, after the reflection functors are sorted, while discussions around this take place before, they forms a circular with connection of morphisms. That is, for \(N=|\text{Ob}(\mathcal{Q})|\),

@@

A morphism in this category means that if the reflection functor on its start is executed just now, then the target functor will be executed next time. That is, to be more specific, if a functor in \(\mathcal{Q}\) has no morphisms targeting it, then it will be never executed unless it is configured as the beginning functor (location \(0\)) manually. Moreover, if a functor has more than one morphisms starting from it, then we call this functor \pmb{ extroverted}. Otherwise, if a functor has more than one morphisms targeting it, it is \pmb{ introverted}. If one has only two morphisms connected, one in and one out, thus it is\pmb{  ordinary}. The process of determining the next functor of a extroverted functor will be discussed below.

@@

\pmb{ Definition. }A recursive functor \(\mathcal{F}_i\) is a functor that applies to pool \(\mathcal{M}_i\) and evolves it into \(\mathcal{M}_{i+1}\). The process of determining which \(\mathcal{K}_w\) is \pmb{ selected} after former reflection functor \(\mathcal{K}_j\) generally works on the knowledge base \(\mathcal{Q}\), right starting from the initial map. If this is the first time for the recursive functor to execute, then \(\mathcal{K}_0\) is selected. If \(\mathcal{F}_i\) encounters with an introverted or ordinary functor \(\mathcal{K}_j\) then significantly,

@@

It is easy to understand that for each reflection functor \(\mathcal{K}_a\) and \(\mathcal{K}_b\), the count of set \(\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_a,\mathcal{K}_b\right)\) indicates the \pmb{ weight} of \(\mathcal{K}_b\) to \(\mathcal{K}_a\), controlling the probability of \(\mathcal{K}_b\) to be selected when the former functor is \(\mathcal{K}_a\). The design of this process is inspired by the lottery scheduling algorithm I learned in Andrew S. Tanenbaum{'}s Operating Systems: Design and Implementation \cite{6} before.

@@

It should be noted that if the initial map does not evolve, the proof efficiency will be primitive. Hence, we define a supplement process called \pmb{ knowledge reinforcement}, with definition coming below.

\pmb{ Definition.} The process of knowledge reinforcement is done after a finishing a proof. The first step of this reinforcement is to add numbers of utilization of the corresponding morphism of copies of morphisms into the knowledge base, increasing the weight of connections between the reflection functors. When next time a proof is issued, the modified knowledge base is \pmb{ loaded} into instance and act as the modified initial situation.

The second step of this sort of reinforcement is called \pmb{ reduction}, which is based on the Ebbinghaus{'}s forgetful curve{'}s numerical fit function. The exact form of the function expression can be found in the Preliminary section. Specifically, the number of morphisms is decreased following the forgetful equation, changing into the nearest integer number. To be more explicit, the Ebbinghaus-reduced decimal is stored separately from the knowledge base and the exact and accurate representation for this is omitted in the paper.

@@

Future works are the followings below:
\begin{itemize}
	\item \pmb{Continuing the implementation of the corresponding software.} Currently the software I developed is still under immature development and many of the aspects I presented in the paper above, including the self-evolution logic, have not been constructed yet.
	\item  \pmb{Improving the algorithm.} The algorithm I presented in the paper is not mature. For instance, if the knowledge base has more than \(2^{3}\) morphisms, then some of the morphisms will never be utilized.
	\item \pmb{Optimizing the performance of the algorithm.} Currently, though the design of the procedures increase generality because of the low-knowledge feature, the performance of derivations may be lower than the current algorithms, which focus on a certain subject inside mathematics.
\end{itemize}

>>>>

%% Copyright 2022 Zijian Wang. All rights reserved.
%% Email: felix_wzj@yahoo.com
%% The newest version can be obtained from GitHub.

@@

To avoid misunderstandings, \textbf{the Zermelo-Fraenkel set theory} or ZFC as short is utilized to be the set system, with Grothendieck universe concepts added. \cite{1}

@@

Before more specific discussion, we select Grothendieck universe \(\mathcal{U}\) \cite{1} to avoid set theory paradoxes. Besides, we define meta category \(\mathcal{C}\) where all discussions take place. There are briefly three kind of objects in \(\mathcal{C}\): symbols, notations and brackets. All symbols in \(\mathcal{C}\) forms sub category \(\text{Sym}(\mathcal{C})\) called the \textbf{ Symbol Subcategory}. All notations in \(\mathcal{C}\) forms \(\text{Not}(\mathcal{C})\) and all brackets forms \(\text{Bra}(\mathcal{C})\), called the \textbf{ Notation Subcategory} and the \textbf{ Bracket Subcategory}. That is,

@@

\pmb{ Definition.} A \textbf{ bracket} \(\beta\) is defined as a set of ordered pairs in the form of below:

@@

\(\beta\) is valid if and only if every element of \(\beta\), its left element is unique. We define filtered subsets of \(\beta\). The \textbf{ Symbol Subset} of \(\beta _{\mathcal{S}}\text{:=}\left\{t\in \beta \left|t_{\mathit{r}}\in \text{Sym}(\mathcal{C})\right.\right\}\). Following this way, the \textbf{ Notation Subset} \(\beta _{\mathcal{N}}\) and the \textbf{ Bracket Subset} \(\beta _{\mathcal{B}}\) are defined as well. There are two types of brackets: The first type is called a \textbf{ Symbol Holder} where \(\beta =\{(i,A)\},i\in \mathbb{Z}_{\geq 1},A\in \text{Sym}(\mathcal{C})\). The second type is called a \textbf{ Compositor} where

@@

\pmb{ Definition.} Two bracket \(\alpha\) and \(\beta\), are thought to be \textbf{ isomorphic} (noted as \(\alpha \simeq \beta\)) if they satisfy the following restrictions:

First, \(|\alpha |=|\beta |\) indicating the two brackets have same cardinal numbers. Second, all right elements sorted in the order defined by the sort of the left pair elements, correspondingly, are either same or symbols with the same type. Otherwise, the two brackets are \textbf{ not isomorphic}, noted as \(\alpha \not{\simeq}\beta\).

@@

\pmb{ Definition.} A \textbf{ notation} \(\mathcal{N}\) is defined as an object in \(\text{Not}(\mathcal{C})\) which is a sub category of \(\mathcal{C}\). The \(\text{Ob}(\text{Not}(\mathcal{C}))\) set can be mapped to \(\text{On}_{\geq 0}\) class, indicating the number of parameters that a notation take. In which,

@@

In that case if \(n=0\) then we say \(\mathcal{N}\) is a \textbf{ type} and if \(n>0\) then \(\mathcal{N}\) is an \textbf{ operator}. For instance, obviously, \(\mathit{p}(+)=2\) and \(\mathit{p}(\neg )=1\). A notation\(\mathcal{N}\) is called \textbf{ finite} if \(\mathit{p}(\mathcal{N})<\omega\), and otherwise \(\mathcal{N}\) can have infinite number of symbols as parameters, when the notation is called to be \textbf{ infinite}.

@@

\pmb{ Definition.} A \textbf{ symbol} \(\mathcal{S}\) is defined as an object in \(\text{Sym}(\mathcal{C})\) which is a sub category of \(\mathcal{C}\). There exists a functor from \(\text{Sym}(\mathcal{C})\) to \(\text{Not}(\mathcal{C})\):

@@

Where \(\nu (\mathcal{S})\) is the \textbf{ corresponding notation} of \(\mathcal{S}\) and must satisfy \(\forall \mathcal{S}\in \text{Sym}(\mathcal{C}),\mathit{p}(\nu (\mathcal{S}))=0\), indicating all corresponding notations are types instead of operators. For convenience and precision, the text that meaning creating a symbol \(\mathcal{S}\) whose corresponding notation is \(\mathcal{N}\)can and should be written in the form below.

@@

Two brackets are thought to be \textbf{ equal} when the sequences of \(t_{\mathit{r}}\), sorted via the ordering of \(t_{\ell }\) are the same and this relationship constructs a equivalence morphism between the two in the \(\text{Bra}(\mathcal{C})\) category, noted as below:

@@

\pmb{ Definition.} A notation \(\mathcal{N}\) is called being \textbf{ inherited} from notation \(\mathcal{M}\) (or we say \(\mathcal{N}\) is\textbf{  a kind of} \(\mathcal{M}\)) when there exists such morphism between the two in \(\text{Not}(\mathcal{C})\):

@@

\[\alpha =\{(0,\text{for}),(1,\beta ),(2,\{(0,<),(1,\{(0,\text{abs}),(1,\pmb{x})\}),(2,\pmb{1})\})\}\]
\[\beta =\{(0,=),(1,\delta ),(2,\{(0,/),(1,\pmb{1}),(2,\{(0,-),(1,\pmb{1}),(2,\pmb{x})\})\})\}\]
\[\delta =\{(0,\sum ),(1,\{(0,=),(1,\pmb{n}),(2,\pmb{1})\}),(2,\pmb{\infty }), (3,\{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\})\}\]

@@

Another issue is about the recognition between majorly two types of brackets: the type of bracket that purely serves as a brick for constructing mathematical expressions and the type of bracket that forms the thing that former mathematics call them statements (for instance, \(\{(0,=),(1,x),(2,y)\}\) or the expression for the Pythagorean theorem). In this system for representation, the second sort of bracket is called \textbf{ micro-statements}, whose precise definition comes below.

@@

It is essential to pay attention to that a bracket with 2-parameter notation is not necessarily a micro-statement. This conclusion can be illustrated via the example of \(\{(0,+),(1,x),(2,y)\}\) whose notation has two symbols as parameters but is not a micro-statement. The second restriction is more important, which is that a micro-statement must have the capacity to be evaluated into a Boolean value, that is, \(\text{true}\) or \(\text{false}\). What is notable, the \textbf{ evaluation} process is not declared inside the representation system, whose definition comes below. All micro-statement brackets forms the \textbf{ Micro-Statement }sub category of \(\text{Bra}(\mathcal{C})\) and is annotated as \(\text{Mic}(\mathcal{C})\).

@@

The Boolean value \(\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m})\in \{0,1\}\) is called the \textbf{ evaluation result} of micro-statement. If for bracket \(\mathit{m}\) exists a morphism to \(\mathcal{B}\) that satisfies the definition of evaluation, then we say that \(\mathit{m}\) is \textbf{ evaluatable}. That is, if it satisfies the first restriction of being a micro-statement as well, it is a micro-statement.

@@

The discussion below calls the \(\text{Mic}(\mathcal{C})\) category the \textbf{ micro-statement pool}, or \textbf{ pool} for short. The morphisms inside the micro-statements pool are declared for representation of implication relationships. It is obvious are elementary that,

@@

\pmb{ Definition.} A \textbf{ derivation} is a set of ordered pairs of ordinals and categories in the form below.

@@

Where \(\mathcal{M}_i\) { }is a micro-statement pool and for each element in \(\mathcal{D}\), its left pair element is a unique ordinal. The $\mathcal{D}$ set is well-ordered following the sort of \(i\). On the beginning, the the initial pool equals to the condition, that is the micro-statements given by the problem. On the other hand, the conclusions of the proof problem, to be proved via some steps form a set \(\mathcal{R}\), called the \textbf{requirement set} are to be inferred to exist inside the micro-statement pool.

@@

\pmb{ Definition.} A \textbf{ step of derivation} is a map existed on the derivation set \(\mathcal{D}\), mapping from a pair to another, whose ordinal increases by \(1\). This map is annotated using script word \(\mathit{s}\mathit{t}\mathit{e}\mathit{p}\). The form is shown below:

@@

Inside the map, the left pair element is simply self-increased and the right pair element is processed by a functor (since the item to process is a category) called the \textbf{ recurse functor} noted as \(\mathcal{F}_i\). That is,

@@

\pmb{ Definition.} A derivation set is thought to be \textbf{ successful} when the condition below is satisfied when the condition below is true:

@@

On the other hand, a derivation set is thought to be \textbf{ impossible} when there does not exist such a \(n\in [0,\omega )\) that makes the requirement set a subset of the object set of the targeted micro-statement pool.

@@

\pmb{ Definition. }A \textbf{ reflection functor} \(\mathcal{K}\) is defined as an functor object in a functor category \(\mathcal{R}\mathit{e}\mathit{f}\), who maps between two micro-statement pools. Because of the Zermelo{'}s Well-Ordering Theorem we mentioned in the Preliminary section, \(\text{Ob}(\mathcal{R}\mathit{e}\mathit{f})\) can be put into well-order, with ordinal \(i\). All of the reflection functors forms a functor category \(\mathcal{Q}\), called the \textbf{ reflection knowledge base}, or for short the \textbf{ knowledge base}. The detailed explanation and description, including the utilization of and morphisms inside the knowledge base, will be discussed later in this section of the paper. We annotate each of the functor positioned at location \(i\) with \(\mathcal{K}_i\).

Each reflection functor corresponds to a \textbf{ template pair} of micro-statements \((\sigma ,\tau )\) which indicates that the effect of the functor is to transform micro-statement \(\sigma\) into $\tau $. The template pair of functor \(\mathcal{K}\) is annotated with \(T(\mathcal{K})\). That
is,

@@

When reflection functor \(\mathcal{K}_i\) is applied to a pool \(\mathcal{M}_i\), each of the micro-statements in the object set of the pool is proceeded. If a micro-statement is suitable for the reflection, whose detailed explanation will be discussed later, a new micro-statement will be created if there{'}s no duplication. Then a morphism will be built from the old micro-statement to the new item. The process of identifying whether a micro-statement is capable called an \textbf{ isomorphism inspection} is described as below.

\pmb{ Definition.} The process of isomorphism inspection is declared as below. The stuff that the isomorphism inspection process manipulates is a micro-statement \(\mu \in \mathcal{M}_i\), a special evaluatable sort of bracket. The definition of bracket being isomorphic can be found in the second section. Explicitly, the inspection process is to construct a new set called the \textbf{ transformation source}, noted as \(\text{Ts}\) using the equation below.

@@

What to do next is called a \textbf{ transformation}. Foremost, creates a set of transformation rules that makes one-one maps the micro-statement to manipulate to the left of the template pair \(\sigma\). Secondarily, the reverse map is applied to the right of the template pair \(\tau\) and then the transformation process execution is done. Then we delineate the definition of { }transformation mapping.

\pmb{ Definition.} A \textbf{ transformation map} is a one-one map defined between the list of symbol and sub-brackets of the two brackets \(\alpha\) and \(\beta\) where,

@@

To begin with, the translation map between the two temporary sets, that is each of the elements of transformation source and the left element of the template pair, are constructed forming an executable rule that makes each non-notation right pair element \(x\) in \(\mu \epsilon \mathcal{M}_i\), which is a micro-statement to discuss, to have \(\mathcal{T}(x)\in \sigma _{\mathcal{B}}\cup \sigma _{\mathcal{S}}\). After the construction, we execute a \textbf{ reverse transformation } from \(\tau\) to a new micro-statement \(\mu '\) satisfying that

@@

\pmb{ Definition. }The \textbf{ initial map }is the original state of knowledge base \(\mathcal{Q}\) when \(\mathcal{Q}\) is created. Initially, after the reflection functors are sorted, while discussions around this take place before, they forms a circular with connection of morphisms. That is, for \(N=|\text{Ob}(\mathcal{Q})|\),

@@

A morphism in this category means that if the reflection functor on its start is executed just now, then the target functor will be executed next time. That is, to be more specific, if a functor in \(\mathcal{Q}\) has no morphisms targeting it, then it will be never executed unless it is configured as the beginning functor (location \(0\)) manually. Moreover, if a functor has more than one morphisms starting from it, then we call this functor \textbf{ extroverted}. Otherwise, if a functor has more than one morphisms targeting it, it is \textbf{ introverted}. If one has only two morphisms connected, one in and one out, thus it is\textbf{  ordinary}. The process of determining the next functor of a extroverted functor will be discussed below.

@@

\pmb{ Definition. }A recursive functor \(\mathcal{F}_i\) is a functor that applies to pool \(\mathcal{M}_i\) and evolves it into \(\mathcal{M}_{i+1}\). The process of determining which \(\mathcal{K}_w\) is \textbf{ selected} after former reflection functor \(\mathcal{K}_j\) generally works on the knowledge base \(\mathcal{Q}\), right starting from the initial map. If this is the first time for the recursive functor to execute, then \(\mathcal{K}_0\) is selected. If \(\mathcal{F}_i\) encounters with an introverted or ordinary functor \(\mathcal{K}_j\) then significantly,

@@

It is easy to understand that for each reflection functor \(\mathcal{K}_a\) and \(\mathcal{K}_b\), the count of set \(\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_a,\mathcal{K}_b\right)\) indicates the \textbf{ weight} of \(\mathcal{K}_b\) to \(\mathcal{K}_a\), controlling the probability of \(\mathcal{K}_b\) to be selected when the former functor is \(\mathcal{K}_a\). The design of this process is inspired by the lottery scheduling algorithm I learned in Andrew S. Tanenbaum{'}s Operating Systems: Design and Implementation \cite{6} before.

@@

It should be noted that if the initial map does not evolve, the proof efficiency will be primitive. Hence, we define a supplement process called \textbf{ knowledge reinforcement}, with definition coming below.

\pmb{ Definition.} The process of knowledge reinforcement is done after a finishing a proof. The first step of this reinforcement is to add numbers of utilization of the corresponding morphism of copies of morphisms into the knowledge base, increasing the weight of connections between the reflection functors. When next time a proof is issued, the modified knowledge base is \textbf{ loaded} into instance and act as the modified initial situation.

The second step of this sort of reinforcement is called \textbf{ reduction}, which is based on the Ebbinghaus{'}s forgetful curve{'}s numerical fit function. The exact form of the function expression can be found in the Preliminary section. Specifically, the number of morphisms is decreased following the forgetful equation, changing into the nearest integer number. To be more explicit, the Ebbinghaus-reduced decimal is stored separately from the knowledge base and the exact and accurate representation for this is omitted in the paper.

@@

Future works are the followings below:
\begin{itemize}
	\item \textbf{Continuing the implementation of the corresponding software.} Currently the software I developed is still under immature development and many of the aspects I presented in the paper above, including the self-evolution logic, have not been constructed yet.
	\item  \textbf{Improving the algorithm.} The algorithm I presented in the paper is not mature. For instance, if the knowledge base has more than \(2^{32}\) morphisms, then some of the morphisms will never be utilized.
	\item \textbf{Optimizing the performance of the algorithm.} Currently, though the design of the procedures increase generality because of the low-knowledge feature, the performance of derivations may be lower than the current algorithms, which focus on a certain subject inside mathematics.
\end{itemize}
